Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-22 lqg-strings.tex
made changes to section VI

while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ implies that

@@

Afshordi's work notes that action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry. We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, thus we postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.

@@

In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$. We now explore this claim: since we're now dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a WS dilaton, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
\begin{equation} \label{eqn:mu0-phi-relation}
	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
\end{equation}
where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.

>>>>

while the auxiliary $\bra{0 ; p} \Hat{\widetilde{L}}_{n , 0} \zeta _{\mu '} (\Hat{a}^{\mu '} _{d})^{\dagger} \ket{0 ; p} = 0$ constraint implies that

@@

Afshordi's work notes that the action \eqref{eqn:emergent-dimensions-action} only has background Poincaré invariance and WS Weyl symmetry as approximate symmetries for the fields with $m_{\mu} \gg T$, thus the \textquotedblleft emergent spacetime and evolving dimensions" by interpreting the fields with effective mass as being inaccessible due to not obeying Poincaré symmetry. We go one step further and note that since eq \eqref{eqn:X-masses-constraint} leaves $m_{0} , m_{1}$ and $m_{2}$ unconstrained, the related dimensions might be regarded as being \emph{fundamental} and thus the true quantum gravitational field should be $(2 + 1)$-dimensional, in agreement with \cite{t-Hooft1993Dimensional}. $(2 + 1)$-dimensional gravity has already been successfully quantized before (\cite{Bergshoeff2013ZweiDreibein},\cite{Blais:2013sdr},\cite{Witten:1988hc},\cite{Carlip:1998uc}). We thus postulate that $m_{3} \sim T_{pl}$, which together with the constraints \eqref{eqn:X-masses-constraint} should give us a way to calculate the other mass parameters given the WS energy and momentum of the fields, making it possible to predict in which scales the other dimensions should start to open up.

@@

In section \ref{sec:inverse-metric-Polyakov} we arrived at eq \eqref{eqn:coupling-X-phi} and claimed the coupling between the WS conformal factor $\phi (x)$ and the embedding fields $X^{\mu}$ to be akin to the dilaton field $\Phi (X)$. We now explore this claim: since we could be dealing with emergent dimensions with an action \eqref{eqn:emergent-dimensions-action} that only has Weyl symmetry as an approximate symmetry, we believe that the conformal factor $\phi (x)$ can be viewed as a \emph{worldsheet dilaton}, which sets the scale of the string dictating which dimensions it can interact with, thus the coupling \textquotedblleft constant" of the masses may be related to the conformal factor
\begin{equation} \label{eqn:mu0-phi-relation}
	\mu _{0} ^2 \sim \e ^{- \phi (x)} ,
\end{equation}
where the minus sign is due to the fact that the dimensions open up at larger and larger scales, so we require a larger and larger string to interact with each new dimension.
